---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.align = "center",
  fig.dim = c(7,4) * 1.4
)
```

# rjd3xjars

<!-- badges: start -->
[![Mentioned in Awesome Official Statistics ](https://awesome.re/mentioned-badge.svg)](https://github.com/SNStatComp/awesome-official-statistics-software)
<!-- badges: end -->

R interface giving access to advanced SA methods (for instance time dependent ARIMA) as implemented in JDemetra+ v3.x.

## Installation

Running rjd3 packages requires **Java 21 or higher**. How to set up such a configuration in R is explained [here](https://jdemetra-new-documentation.netlify.app/#Rconfig)


You can install the development version of **rjd3xjars** from [GitHub](https://github.com/) with:

```{r, echo = TRUE, eval = FALSE}
# install.packages("remotes")
remotes::install_github("rjdverse/rjd3xjars")
```


## Package Maintenance and contributing

Any contribution is welcome and should be done through pull requests and/or issues.
pull requests should include **updated tests** and **updated documentation**. If functionality is changed, docstrings should be added or updated.


## Licensing

The code of this project is licensed under the [European Union Public Licence (EUPL)](https://interoperable-europe.ec.europa.eu/collection/eupl/eupl-text-eupl-12).
